---
title: "Creating graphs in R with 'ggplot2'"
author: "Shona Lamoureaux"
date: today
date-format: DD MMMM YYYY
format: html
code-fold: true
editor: visual
Theme: flatly
smooth-scroll: true
toc: true
toc-location: left
embed-resources: true
---

## Plots with ggplot2

How to make plots in R using ggplot 2

### Let's load the packages we will be using

```{r}
#| label: load packages
#| output: false
library(tidyverse)
library(readxl)
library(here)
```

The `output: false` option disables the printing of output messages but the code is still displayed.

### Now let's load the data we will use 1st

```{r}
#| label: load np data
#| output: false
ca_np <- read_csv(here("data", "ca_np.csv"))
names(ca_np)
head(ca_np)
summary(ca_np)
ci_np <- read_excel(here("data", "ci_np.xlsx"))
names(ci_np)
head(ci_np)
summary(ci_np)
```

### The first ggplot graph: Visitors to Channel Islands National Park

```{r}
#| label: Plot CI data
```

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
